Who are Toronto’s Crime Victims? A Gender and Crime Type Analysis from 2014 to 2023

### 2024-09-26 paper/paper.qmd
updated title and added Table 1 in appendix

---
title: "Analysis of Crime Victims by Type and Gender from 2014 to 2023"
author: 
  - Kevin Roe
thanks: "All data, R code, and other files are available in the following GitHub repository: <https://github.com/Kanghyunroe/victims_of_crimes/tree/master>"
date: today
date-format: long
abstract: "This paper analyzes data from the Police Annual Statistical Report – Victims of Crime for the years 2014 to 2023 in the City of Toronto. The paper reveals there are 2% more male victims overall, but women are disproportionately affected in certain crime categories: female victims outnumber males by 78 percentage points in sexual crimes and by 9 percentage points in other crimes. These differences show how vulnerability to specific crimes varies by sex. Further research should focus on victims of fatal crimes to explore these disparities."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

#### Loading packages ####
#install.packages("scales")
#install.packages("tidyverse")
# You can and should cross-reference sections and sub-sections. We use @talia, @opendatatorotno, and @rohan.
# The remainder of this paper is structured as follows. @sec-mydatasection
library(tidyverse)
library(ggplot2)
library(scales)

@@

>>>>

---
title: "Who are Toronto’s Crime Victims? A Gender and Crime Type Analysis from 2014 to 2023"
author: 
  - Kevin Roe
thanks: "All data, R code, and other files are available in the following GitHub repository: <https://github.com/Kanghyunroe/victims_of_crimes/tree/master>"
date: today
date-format: long
abstract: "This paper analyzes data from the Police Annual Statistical Report – Victims of Crime for the years 2014 to 2023 in the City of Toronto. The paper reveals there are 2% more male victims overall, but women are disproportionately affected in certain crime categories: female victims outnumber males by 78 percentage points in sexual crimes and by 9 percentage points in other crimes. These differences show how vulnerability to specific crimes varies by sex. Further research should focus on victims of fatal crimes to explore these disparities."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

#### Loading packages ####
#install.packages("scales")
#install.packages("tidyverse")
# You can and should cross-reference sections and sub-sections. We use @talia, @opendatatorotno, and @rohan.
# The remainder of this paper is structured as follows. @sec-mydatasection
library(tidyverse)
library(ggplot2)
library(scales)
library(knitr)

@@

## Data Sample {#sec-appendix-sample}

```{r}
#| label: tbl-head
#| tbl-cap: First 5 rows of cleaned data 
#| echo: false
#| warning: false
#| message: false

#### Table Example ####
cleaned_data |>
  slice(1:5) |>
  kable(
    digits = 1,
    booktabs = TRUE,
    linesep = ""
  )
